Make any stupid plot you want

### 2020-12-03 draft/sections/math.tex
putting in rest of fiber bundle defintion

@@

\subsection{Data Model}
\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

As illustrated by figure~\ref{fig:fiberbundle}, the vertical lines $F$ are the range of possible temperature values embedded in the total space $E$. The base space $K$ of the fiber bundle describes the connectivity of the points in $E$; in figure~\ref{fig:fiberbundle} the connectivty of the timeseries is encoded in the line representation of $K$. The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. 
The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$.
%%% include diagram here of formal definition of sigma

The space of all $\sigma$ is $\Gamma$  (Pull this back into more specific about fig, the general is making this more confusing.)

@@

\subsubsection{Fiber Space $F$}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}
%%% might 
The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text{ where } 0\leq x \leq 1
\end{equation}

@@

The measurement spaces $X$ are each variables and have the properties of measurement scales, such as Steven's nominal, ordinal, interval, and ratio \cite{stevensTheoryScalesMeasurement1946}. 
Spivak provides a formal way of attaching a name to each $X \in F$ and mapping from the value back to the variable type by formulating $E$ in terms of databases \cite{spivakSIMPLICIALDATABASES}. He defines a total space $U$, analogous to $E$, that is the disjoint union of all possible elements of all possible types

For example, the interval $[T_{min}, T_{max}]$ is a restriction on $\mathbb{R}$ that is part of the definition of a type named $\mathrm{Temperature}$ and  $[t_{min}, t_{max}]$ is a restriction on $\mathbb{R}$ that is part of a definition of a type named $\mathrm{Time}$. As in the case of $E$ embedding the $F$ on which these values live, $U$ contains all pairs of all values of these types $U \coloneqq (\mathrm{Temperature}, \mathrm{Time})$. Spivak defines U as being over the space of $\mathrm{DT}$, which is the space of data types $\mathrm{DT} = \{\mathrm{Temperature}, \mathrm{Time}}$.

@@

\subsubsection{Visual Characteristics}
Tau can preserves the measurement type properties (group scales)

Tau is fully flexible and can do whatever; knows about fiber \& neighborhood of fiber. Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k. 
\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$:
\begin{equation}
    \begin{tikzcd}
        A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
        A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
    \end{tikzcd}
\end{equation}

>>>>

\begin{equation}
    A: \sigma \rightarrow \rho
\end{equation}

@@

\subsection{Data Model}

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a structure $(E, K, \pi, F)$  consisting of topological spaces $E, K, F$ and the map from total space to base space $\pi: E \rightarrow K$.

@@

By definition, every point in the base space $k \in K$ has a local neighborhood $U$ such that \pi()
\cite{rowlandFiberBundle,FiberBundle2020}

\begin{tikzcd}
    \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
    U                                                                         &                                         
\end{tikzcd}

There is a bijection from the fiber $F$ to the fiber $F_k$ over the point $k \in K$ such that 
\begin{equation}
\end{equation}

The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$

\begin{tikzcd}
    F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                      & K \arrow[u, "\sigma", description, bend right]
\end{tikzcd}

such that it is the right inverse of $\pi$:
\begin{equation}
    \pi(\sigma(k)) = k \text{ for all } \k \in K 
\end{equation}

In a locally trivial fiber bundle, $\sigma = K \times E$   \cite{weissteinFiberBundle}
\begin{equation}
\sigma(k) = (k, g(k))
\end{equation}

where the fiber at $k$, $F_k$,  is the domain of $g(k)$.  The space of global sections $\sigma$ of $E$ is $\Gamma(E)$:

\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

As illustrated by figure~\ref{fig:fiberbundle}, the vertical lines $F$ are the range of possible temperature values embedded in the total space $E$. The base space $K$ of the fiber bundle describes the connectivity of the points in $E$; in figure~\ref{fig:fiberbundle} the connectivty of the timeseries is encoded in the line representation of $K$.

@@

K is a triangulizable topological space.

\subsubsection{Fiber Space $F$}
The fiver ver is the set of elements $e \in F$ that lies over 
$F_{k}$ is a fiber over $K$ that lo

Spivak provides a formalization for the values $x \in X$ whereby they can have specialized types. He defines the space of datatypes $\mathrm{DT}$

DT = set of strings names of types
U = set of single elements of type in DT
pi (U-DT)
Also need to take column names (U cross C)

# C is more about naming types to reuse primatives

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}
%%% might 
The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text{ where } 0\leq x \leq 1
\end{equation}

@@

% datetime type, columns = start, end

% schema is ordered list of Column, type is approx F, U cross C over sigma, 
% space of rows/records f:k -> r, sigma:k -> r, is the table function (dataframe as instance)

@@

\subsubsection{Visual Encodings}
Tau can preserves the measurement type properties (group scales)

%%The measurement spaces $X$ are each variables and have the properties of measurement scales, such as Steven's nominal, ordinal, interval, and ratio \cite{stevensTheoryScalesMeasurement1946}. Stevens talks about measurements and this is how we define it here:.... can check symmatry under stevens via carry through on tau

Tau is fully flexible and can do whatever; knows about fiber \& neighborhood of fiber. Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k.

%%hatches can either grow the R space or function

\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$:
\begin{equation}
    \begin{tikzcd}
        A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
        A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
    \end{tikzcd}
\end{equation}
